Manuscript title here

### 2025-11-17 manuscript.qmd
Flowchart

dir.create("assets", showWarnings = FALSE)

@@

knitr::include_graphics(out_png)

@@

Descriptive data
----------------

(a) Give characteristics of study participants (eg demographic,
clinical, social) and information on exposures and potential
confounders

@@

(c) Cohort study — Summarise follow-up time (eg, average and total
amount)

Outcome data
------------

Cohort study — Report numbers of outcome events or summary measures
over time

@@

Cross-sectional study — Report numbers of outcome events or summary
measures

Main results
------------

(a) Give unadjusted estimates and, if applicable, confounder-adjusted
estimates and their precision (eg, 95% confidence interval). Make
clear which confounders were adjusted for and why they were included

@@

(c) If relevant, consider translating estimates of relative risk into
absolute risk for a meaningful time period

Other analyses 
--------------

Report other analyses done—eg analyses of subgroups and interactions,
and sensitivity analyses 
-->

@@

Key results
-----------
Summarise key results with reference to study objectives

Limitations
-----------

Discuss limitations of the study, taking into account sources of
potential bias or imprecision.  Discuss both direction and magnitude
of any potential bias

Interpretation
--------------

Give a cautious overall interpretation of results considering
objectives, limitations, multiplicity of analyses, results from
similar studies, and other relevant evidence

Generalisability
----------------

Discuss the generalisability (external validity) of the study results

-->

>>>>

@@

@@

![**Figure 1. Flowchart of patient selection for the analytical cohort**](assets/flowchart.png)

## Descriptive data

<!--  
(a) Give characteristics of study participants (eg demographic,
clinical, social) and information on exposures and potential
confounders

@@

(c) Cohort study — Summarise follow-up time (eg, average and total
amount)
-->
## Outcome data

<!--  
Cohort study — Report numbers of outcome events or summary measures
over time

@@

Cross-sectional study — Report numbers of outcome events or summary
measures
-->

##  Main results

<!--  
(a) Give unadjusted estimates and, if applicable, confounder-adjusted
estimates and their precision (eg, 95% confidence interval). Make
clear which confounders were adjusted for and why they were included

@@

(c) If relevant, consider translating estimates of relative risk into
absolute risk for a meaningful time period
-->

## Other analyses

<!--  
Report other analyses done—eg analyses of subgroups and interactions,
and sensitivity analyses 
-->

@@

## Key results

<!--
Summarise key results with reference to study objectives
-->

## Limitations

<!--
Discuss limitations of the study, taking into account sources of
potential bias or imprecision.  Discuss both direction and magnitude
of any potential bias
-->

## Interpretation

<!--
Give a cautious overall interpretation of results considering
objectives, limitations, multiplicity of analyses, results from
similar studies, and other relevant evidence
-->

## Generalisability

<!--
Discuss the generalisability (external validity) of the study results
-->
